Ground state energy of quantum dots using the coupled cluster method

### 2018-06-06 project_2/article/article.tex
Start on discussion

>>>>

\section{Discussion}

	\subsection{Validity of results}
        All of our results have been compared with the master thesis of M. P.
        Lohne\cite{lohne2010coupled} for up to 10 shells. Lohne gets two sets of
        energies, one set from RHF and one set from CCSD code with harmonic
        oscillator basis functions. Our CCD code with Hartree-Fock basis will
        for some configurations\footnote{By configurations we mean frequency
        $\omega$ and number of particles $N$.} beat CCSD with plain harmonic
        oscillator basis. For 12 shells we can compare with the results from M.
        P. Lohne et al.\cite{lohne2011ab}, but in this article an
        \emph{effective interaction} for the Hamiltonian with a CCSD code has
        been used. These results are therefore significanlty better than ours,
        but we can get a ``ball-park'' idea to benchmark against.

    \subsection{Convergence trouble}
        For a large number of particles and a low frequency the CCD-method get
        trouble with convergence. This happens as the confining potential $v
        \propto \omega^2$ will not be able to confine the particles when the
        interaction gets too strong. The CCD-method will in particular get a
        hard time keep the particles together as the excitation operator $t$
        only excites pairs of particles leading too strong increase in the
        interaction when the particles increase their energy level. This effect
        can potentially be somewhat alleviated by including the singles
        excitation, e.g., using the CCSD-method.

	\subsection{Sparse implementation}
